---
title: "MA331HW1"
author: "Eric Stazzone"
date: "9/5/2020"
output: pdf_document
---

I pledge my honor that I have abided by the Stevens Honor System.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width="50%", out.height = "50%")
```
Problem 1:

Table of X and Y
```{r nums}
x <- c(.2, 1.2, .9, 2.2, 3.2, .3, 1.7, 3.1, 2.3, 1.5, 2.5, 3, 2.6, 9)
y <- c(1.1, 2.3, 1.1, 3.6, .1, 1.0, 6.9, 4.8, 6.5, 7.8, 5.8, 8, 9.4, 9.8)
```
(i) Histogram of X
```{r 1, echo=FALSE}
hist(x, xlim=c(0,10), breaks=9)
```

(i) Pie Chart of Y
```{r 2, echo=FALSE}
pie(y)
```

(ii) Box Plot, Five Number Sum, and Variances of X and Y respectively.
```{r 3, echo=FALSE}
boxplot(x)
```
```{r 4}
fivenum(x)
var(x)
```
There is an outlier, "9", of x.

(ii) Box Plot for Y
```{r 5, echo=FALSE}
boxplot(y)
```
```{r 6}
fivenum(y)
var(y)
```
There is no outlier for y.

(iii) Scatter Plot of (X,Y)
```{r 7, echo=FALSE}
plot(x,y)
```

The correlation coefficient between X and Y is `r cor(x,y)`.
The linear association between X and Y is positive and weak, where X increases at a slower rate than Y.

(iv) X and Y without the outlier
```{r 8}
xout <- c(.2, 1.2, .9, 2.2, 3.2, .3, 1.7, 3.1, 2.3, 1.5, 2.5, 3, 2.6)
yout <- c(1.1, 2.3, 1.1, 3.6, .1, 1.0, 6.9, 4.8, 6.5, 7.8, 5.8, 8, 9.4)
```
The correlation coefficient between X and Y is `r cor(xout,yout)`.

(v) The difference between iii and iv was .109, where the difference was visible when the outlier in iii dictated the trend to have a greater slope.

(vi) Normal QQ plot for Observations of X and Y respectively
```{r 9, echo=FALSE}
qqnorm(flm)
```

Y is more likely to be of a normal distribution.